---
title: "Codebook Wave VII Maghreb"
author: "Hamed Ahmadi"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
```

```{r, echo=FALSE}
df <- read_csv('WAVE_VII_Maghreb.csv')
```

#### Overview of Data:
The Wave VII Maghreb dataset derives from Arab Barometer's Wave VII survey, focusing on the Maghreb region—Algeria, Mauritania, Morocco, and Tunisia. This dataset includes cleaned and coded responses from adults aged 18 and above, providing insights into the socio-political sentiments within these countries.

#### Sources and Methodology:
Data is sourced from Arab Barometer's Wave VII survey, renowned for its robust methodology ensuring national representativeness and reliability. Our dataset has undergone extensive cleaning and coding, aligning with Arab Barometer's technical reports to maintain data integrity and reliability. Surveys were conducted via PAPI, CAPI, and phone interviews, employing multistage probability sampling.

#### Note on Missing Values:
Missing values are noted where responses were not provided, or the data was not applicable. These are coded as 'NA' within the dataset and should be considered during analysis to avoid skewing results.

#### Itemized Presentation of Variables:  

**Variable: Country Name (c_name)**  
- Type: Character  
- Description: Country of the respondent's residence  
- Values: Algeria, Mauritania, Morocco, Tunisia  


**Variable: Source Indication (source)**  
- Type: Factor  
- Description: Method of data collection  
- Values and Frequency:  

**Variable: Respondent Identifier (r_id)**  

Type: Numeric  
Description: Unique ID for each respondent.  

**Variable: Interview Year (r_year)**  

Type: Numeric  
Description: Year of the interview.  
Summary Statistics:  


**Variable: Interview Month (r_month)**  

Type: Numeric  
Description: Month of the interview.  


**Variable: Gender of Respondent (r_female)**  

Type: Factor  
Description: Gender of the respondent.  
Values and Frequency:  

```{r, echo=FALSE}
knitr::kable(table(df$r_female), caption = "Frequency of Gender")
```


**Variable: Political Interest (p_interest)**  

Type: Factor  
Description: Respondent's interest in politics   
Values and Frequency:     

```{r, echo=FALSE}
knitr::kable(table(df$p_interest), caption = "Frequency of Political Interest Levels")
```


**Variable: Economic Evaluations (p_economy)**  

Type: Factor  
Description: Respondent's view of the economy.  
Values and Frequency:  

```{r, echo=FALSE}
knitr::kable(table(df$p_economy), caption = "Frequency of Economic Evaluations")
```



**Variables: Satisfaction with Democracy (Q516_1 to Q516_4)**  

Type: Factor  
Description: Respondents' agreement or disagreement with statements about the performance and characteristics of democratic systems.

Q516_1: "Under a democratic system, the country's economic performance is weak."  
Q516_2: "Democratic regimes are indecisive and full of problems."  
Q516_3: "Democratic systems are not effective at maintaining order and stability."  
Q516_4: "Democratic systems may have problems, yet they are better than other systems."  

Values and Frequency:  

```{r, echo=FALSE}

satisfaction_with_democracy <- df[, grep("Q516", names(df))]
knitr::kable(sapply(satisfaction_with_democracy, table), caption = "Frequency of Satisfaction with Democracy")

```



